Supplementary Materials

### 2023-07-06 manuscript/supplementary.tex
ms changes
sup tbl

@@

>>>>

\subsection{Strong Selection Non-Identifiability}
\label{supp:}

\begin{figure}[htbp]
    \label{suppfig:sel-ident}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/ave_sel_vs_pi0.pdf}
  \caption{XXX}
\end{figure}

@@

\subsection{Average Selection Coefficients}

There are the average selection coefficients ($\bar{s}$) calculated from the
estimated DFEs, across both default and constrained grids.

\begin{tabular}{|l|llrr|}
\hline
Annotation Model &  Population &    Feature &   ${\bar{s}}$ (default grid) & ${\bar{s}}$ (constrained grid) \\
\hline
 PhastCons Priority &  CEU &        CDS &  0.100000 &  0.000000 \\
 PhastCons Priority &  CEU &       gene &  0.005308 &  0.000226 \\
 PhastCons Priority &  CEU &  PhastCons &  0.008076 &  0.006275 \\
 PhastCons Priority &  CHB &        CDS &  0.100000 &  0.000000 \\
 PhastCons Priority &  CHB &       gene &  0.004896 &  0.000296 \\
 PhastCons Priority &  CHB &  PhastCons &  0.001327 &  0.005886 \\
 PhastCons Priority &  YRI &        CDS &  0.000000 &  0.000000 \\
 PhastCons Priority &  YRI &       gene &  0.005556 &  0.000160 \\
 PhastCons Priority &  YRI &  PhastCons &  0.028642 &  0.007575 \\
   Feature Priority &  CEU &        CDS &  0.075041 &  0.005281 \\
   Feature Priority &  CEU &       gene &  0.001654 &  0.000315 \\
   Feature Priority &  CEU &  PhastCons &  0.069563 &  0.008767 \\
   Feature Priority &  CHB &        CDS &  0.074797 &  0.005211 \\
   Feature Priority &  CHB &       gene &  0.001974 &  0.000271 \\
   Feature Priority &  CHB &  PhastCons &  0.051988 &  0.008507 \\
   Feature Priority &  YRI &        CDS &  0.054503 &  0.001576 \\
   Feature Priority &  YRI &       gene &  0.001912 &  0.000336 \\
   Feature Priority &  YRI &  PhastCons &  0.055153 &  0.009369 \\
            CADD 6\% &  CEU &      CADD 6\% &  0.042458 &  0.006500 \\
            CADD 6\% &  CHB &      CADD 6\% &  0.031565 &  0.005733 \\
            CADD 6\% &  YRI &      CADD 6\% &  0.043671 &  0.007926 \\
            CADD 8\% &  CEU &      CADD 8\% &  0.041254 &       - \\
            CADD 8\% &  CHB &      CADD 8\% &  0.029052 &       - \\
            CADD 8\% &  YRI &      CADD 8\% &  0.046212 &       - \\
\hline
\end{tabular}
